Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
intro

In this paper we instead focus on time-independent models,
neglecting radiative cooling.  This approach allows us to
systematically explore the relevant parameter space and to derive
analytic expressions that prove useful in determining whether
cooling instabilities manifest across the expected range of galaxy
properties, or whether other (non-AGN) forms of feedback can produce a prolonged state of steady, thermally stable accretion.  Even if cooling instabilities develop on galactic scales over longer $\sim$ Gyr timescales, a quasi steady-state  may exist between these inflow events on
smaller radial scales comparable to the sphere of influence.  We are
thus motivated to explore whether such steady flows are generally expected within the
nucleus under, or whether in most galaxies the nuclear gas content is always
building towards instability.
%A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.

In the presence of strong heating, one-dimensional steady-state flow
is characterized by an inflow-outflow structure, with a critical
radius known as the``stagnation radius" $\rs$ where the radial
velocity passes through zero.  Mass loss from stars interior to the
stagnation radius is accreted, while that outside $\rs$ is unbound in
an outflow from the nucleus.  The stagnation radius, rather than the
Bondi radius, thus controls the SMBH accretion rate (although we will
show that $\rs$ will in many cases resides near the nominal Bondi
radius).  When heating is sufficiently weak, however, the stagnation
radius may move to much larger radii or not exist at all, in which case the entire ISM of the galaxy is flowing
towards the SMBH.  A goal of this work is to assess under what
conditions a stagnation radius exists, as this question is intimately
tied to that of cooling instability.
% Furthermore, in some cases we find that no stagnation
% radius exists at all; this formally implies that the entire of ISM of
% the galaxy is feeding the SMBH, potentially resulting in much higher
% accretion rate than would be predicted by simple Bondi accretion.

>>>>

In this paper we instead focus on time-independent models, with
sufficient heating to have negligible radiative cooling.  This
approach allows us to systematically explore the relevant parameter
space and to derive analytic expressions that prove useful in
determining whether cooling instabilities manifest across the expected
range of galaxy properties, or whether other (non-AGN) forms of
feedback can produce a prolonged state of steady, thermally stable
accretion.  Even if cooling instabilities develop on galactic scales
over longer $\sim$ Gyr timescales, a quasi steady-state may exist
between these inflow events on smaller radial scales comparable to the
sphere of influence.  We are thus motivated to explore whether such
steady flows are generally expected within the nucleus under, or
whether in most galaxies the nuclear gas content is always building
towards instability.
%A chief goal of our analysis is to provide a framework for interpreting the properties of quiescent galactic nuclei given the comparatively well understood physics of stellar winds and supernova heating.

In the presence of strong heating, one-dimensional steady-state flow
is characterized by an inflow-outflow structure, with a critical
radius known as the``stagnation radius" $\rs$ where the radial
velocity passes through zero.  Mass loss from stars interior to the
stagnation radius is accreted, while that outside $\rs$ is unbound in
an outflow from the nucleus.  The stagnation radius, rather than the
Bondi radius, thus controls the SMBH accretion rate (although we will
show that $\rs$ will in many cases resides near the nominal Bondi
radius).  When heating is sufficiently weak, however, the stagnation
radius may move to much larger radii or not exist at all, in which
case nearly entire ISM of the galaxy is flowing towards the SMBH.  A goal
of this work is to assess under what conditions a stagnation radius
exists, as this question is intimately tied to that of cooling
instability.
